A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-28 paper/fascd.tex
Just change a few words

\title{A full approximation scheme multilevel method \\ for nonlinear variational inequalities\thanks{Draft \today.%Submitted to the editors DATE.
\funding{EB was supported by a Faculty Development Travel Award from United Academics, University of Alaska Fairbanks. PEF was supported by the Engineering and Physical Sciences Research Council [EPSRC grants EP/R029423/1 and EP/W026163/1]. This work used the ARCHER2 UK National Supercomputing Service (https://www.archer2.ac.uk). PEF thanks Lawrence Mitchell for advice on implementation, and Jack D.~Betteridge for assistance with numerical Example \ref{ex:results:sia}.}}}

@@

All iterates in FASCD, on all mesh levels, are admissible, and thus the nonlinear operator in the VI needs only be defined for admissible states.  For example, we solve an ice sheet geometry problem (Examples \ref{ex:sia} and \ref{ex:results:sia}) in which the ice flow formulas are only meaningful for surface elevation iterates that do not penetrate the bedrock.  (Non-admissible methods, including semi-smooth methods \cite{BensonMunson2006}, would require unnatural modifications of the operator formula.)  FASCD solves this low-regularity ice sheet problem, wherein the solution has unbounded gradient at the free boundary, by a small, mesh-independent number of F-cycle iterations (Example \ref{ex:results:sia}).  The same Example demonstrates the parallel weak scaling \cite{Bueler2021} of our implementation.

@@

Firedrake applications can exploit the PETSc \cite{Balayetal2023} library's parallel solvers.  The above Examples, which were run in serial to fix the smoother, also run efficiently in parallel.  The next Examples apply parallel solvers and then demonstrate the weak scaling of FASCD F-cycles.

>>>>

\title{A full approximation scheme multilevel method \\ for nonlinear variational inequalities\thanks{Draft \today.%Submitted to the editors DATE.
\funding{EB was supported by a Faculty Development Travel Award from United Academics, University of Alaska Fairbanks. PEF was supported by the Engineering and Physical Sciences Research Council [EPSRC grants EP/R029423/1 and EP/W026163/1]. This work used the ARCHER2 UK National Supercomputing Service (https://www.archer2.ac.uk). PEF thanks Lawrence Mitchell for advice on implementation, and Jack D.~Betteridge for assistance with Example \ref{ex:results:sia}.}}}

@@

All iterates in FASCD, on all mesh levels, are admissible, and thus the nonlinear operator in the VI needs only be defined for admissible states.  For example, we solve an ice sheet geometry problem (Examples \ref{ex:sia} and \ref{ex:results:sia}) in which the ice flow formulas are only meaningful for surface elevation iterates that do not penetrate the bedrock.  (Non-admissible methods, including semi-smooth methods \cite{BensonMunson2006}, would require unnatural modifications of the operator formula.)  FASCD solves this low-regularity ice sheet problem, wherein the solution has unbounded gradient at the free boundary, by a small, mesh-independent number of F-cycle iterations (Example \ref{ex:results:sia}). The same Example investigates the parallel weak scaling \cite{Bueler2021} of our implementation.

@@

Firedrake applications can exploit the PETSc \cite{Balayetal2023} library's parallel solvers.  The above Examples, which were run in serial to fix the smoother, also run efficiently in parallel.  The next Examples apply parallel solvers and investigate the weak scaling of FASCD F-cycles.
